Draft

### 2017-09-03 Thesis/Draft.Rmd
Add corollary for lower bound

---
title: "Draft"
header-includes:
   #- \documentclass[a4paper,twoside,english]{article}
   - \usepackage[retainorgcmds]{IEEEtrantools}
   - \usepackage{bm}
   - \usepackage{amsmath}
   - \usepackage{bbm}
   - \usepackage{hyperref}
   - \usepackage[lined,boxed]{algorithm2e}
   - \newtheorem{theorem}{Theorem}
   - \newtheorem{definition}{Definition}
   - \newtheorem{lemma}{Lemma}
   - \newcommand{\KL}{\,\text{KL}}
   - \newcommand{\der}{\,\text{d}}
   - \newcommand*{\Alignyesnumber}{\refstepcounter{equation}\tag{\theequation}}%
   #- \usepackage[top=1.5cm, bottom=1.5cm, outer=5cm, inner=2cm, heightrounded, marginparwidth=2.5cm, marginparsep=2cm]{geometry}
   #- \usepackage{fontspec}
   #-   \setmainfont{Arial}
keep_tex: TRUE
output:
  pdf_document:
    number_sections: true
    keep_tex: true
    toc: true
    toc_depth: 2
    #latex_engine: xelatex
fontsize: 11pt
urlcolor: blue
---

@@

\IncMargin{1em}
\begin{algorithm}
\SetKwData{Left}{left}\SetKwData{This}{this}\SetKwData{Up}{up}
\SetKwFunction{Union}{Union}\SetKwFunction{FindCompress}{FindCompress}
\SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
\Input{$\tau$, $\epsilon$}
\Output{$\hat{S}_{\tau} = \{k: \hat{\mu}_k(T) \geq \tau\}$}
\BlankLine
\emph{Pull each arm once}\;
\For{$t = K+1$ \KwTo $T$}{
  \emph{Pull arm $I_t = \arg \min_{k\leq K} B_k^{APT}(t) = \sqrt{T_k(t)} (|\hat{\mu}_i(t) - \tau|+\epsilon)$}\;
  \emph{Observe reward $X \sim \nu_{I_t}$}\;
}
\caption{Anytime Parameter-free Thresholding Algorithm (Locatelli et al., 2016)}\label{alg:APT}
\end{algorithm}\DecMargin{1em}

@@

As noted in Zhong et al. (2017), a simple requirement to correctly classify arms at the final round is the following. For every arm $i \in \{1, ..., K\}$ after the final round $T$, require
$$
\hat{\mu}_{i,T_i(n)} \geq \mu_i - \frac{\mu_i - \tau + \epsilon}{2} \quad \text{if} \quad \mu_i \geq \tau
$$
or
$$
\hat{\mu}_{i,T_i(n)} \leq \mu_i + \frac{\tau - \mu_i + \epsilon}{2} \quad \text{if} \quad \mu_i < \tau
$$
Or simply in terms of the gap between the arm and the threshold as used in the index by the APT algorithm:
$$
| \hat{\mu}_{i, T_i(n)} - \mu_i | \leq \frac{|\mu_i - \tau| + \epsilon}{2} = \frac{\Delta_i}{2}.
$$

Intuitively, this condition makes sense as it ensures that the current mean estimate is closer to the true mean than to the threshold. Consequently, there is no arrangement possible in which the arm is classified wrong while the separation condition holds. Assuming $\mu_i < \tau$ and $\epsilon = 0$, an incorrect classification would require $\mu_i < \tau \leq \hat{\mu_i}$. But then  $| \hat{\mu}_{i, T_i(n)} - \mu_i | \geq |\mu_i - \tau|$, which violates the separation condition.

@@

Furthermore, we have assumed $T>2K$ in the statement of Theorem \ref{theorem:LocatelliTheorem4}. Plugging this in gives 
$$
T_k(T) - 1 \geq \frac{(T-K)h_k}{H} \geq \frac{(T-1/2T)h_k}{H} = \frac{Th_i}{2H}
$$

@@

$$
T_k(t) \geq T_k(T) - 1 \geq \frac{Th_i}{2H}.
$$

@@

$$
\mathbb{E}[L] = 1 - \mathbb{P}(\xi) \leq 2(\log(T)+1)K \exp(-\frac{1}{64R^2}\frac{T}{H}).
$$

@@

When introducing the thresholding bandit setting, we did not mention the fact that the budget $T$ does not need to be fixed upfront. Indeed, the setting in which the budget is *not* fixed upfront might be more popular among the best arm identification and top-$m$ literature. This setting is called *fixed-confidence*, while the setting we considered so far is called *fixed-budget*. In the fixed-budget setting, we run algorithms for $T$ samples and then compare them based on their expected loss, $\mathbb{E}[\mathcal{L}(T)] = \mathbb{P}(\mathcal{S}^*_m \neq \hat{\mathcal{S}}_m) =: p_t(\nu)$ as we have seen in $\autoref{sec:Setup}$. Alternatively, consider a $\delta$-PAC strategy $\mathcal{A}(\delta)$for which holds for every problem $\nu \in \mathcal{M}_m$ that the classification holds at least with confidence level $1-\delta$, that is, $\mathbb{P}(\mathcal{S}^*_m = \hat{\mathcal{S}}_m) \geq 1-\delta$. The strategy has to achieve this level of confidence in its prediction before it is allowed to stop sampling. This is the fixed-confidence case, in which the budget $T$ is no longer fixed upfront, but becomes a random variable. We compare algorithms by their expected number of draws $\mathbb{E}_{\nu}[T_{\delta}]$ and prefer those which arrive at the confidence level $1-\delta$ with a smaller expected budget.

@@

To prove this statement, we assume as before that the arms are ordered by their means decreasing in size. For a given $\delta$-PAC algorithm $\mathcal{A} = ((A_t), \tau, \hat{S}_m)$, and under the continuity conditions (compare Kaufmann et al. (2016)), there exists for every arm $a \in \{1, \dots, K\}$ an alternative model $\nu' = (\nu_1, \dots, \nu_{a-1}, \nu_a', \nu_{a+1}, \dots, \nu_K)$. In this alternative model, only arm $a$ is modified in accordance with the continuity conditions. Modified in such a way, the arm $\nu_{m+1}$ is now closer to $\nu_a$ as measured by the Kullback-Leibler divergence than $\nu_a'$ is to $\nu_a$, if $\mu_a > \mu_{m+1}$ (consequently, $\mu_a' < \mu_{m+1}$). On the other hand, if $\mu_a < \mu_{m}$, then $\nu_a'$ will be moved away from $\nu_a$ just enough so that $\nu_a$ is closer to $\nu_m$ than to $\nu_a'$ (consequently, $\mu_a' > \mu_m$). These changes in distribution make the original set of optimal arms, $\{1,\dots,m\}$, no longer optimal under the alternative model $\nu'$. Given that the algorithm returns $\hat{S}_m$, we know that for the event $\mathcal{E} = (\hat{S}_m = \{1, \dots, m\})$ (which is element of the $\sigma$-Algebra $\mathcal{F}_{\tau}$ induced by the stopping time $\tau$), that $\mathbb{P}_{\nu}(\mathcal{E}) \geq 1-\delta$ and $\mathbb{P}_{\nu'}(\mathcal{E}) \leq \delta$ (because fixed confidence $\delta$!).

To now give the lower bound on the expected number of samples, $\mathbb{E}_{\nu}[\tau]$, we employ the general Lemma given by the authors for such changes in distribution in bandit models.

@@

\begin{equation*}
\mathbb{E}_{\nu}[\tau] = \sum_{a=1}^K \mathbb{E}_{\nu}[N_a] \geq \Big( \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m]})} \Big) \der(1-\delta, \delta)
\end{equation*}

Given that we will be naturally interested in either very high or very low confidence of our algorithm, that is, $P_\nu(\mathcal{E})$ is either close to 0 or 1, it is possible to use the following approximation to the binary relative entropy:

\begin{equation}\label{bre_approx}
\forall x \in [0,1], \quad \der(x,1-x) = \der(1-x,x) \geq \log \frac{1}{2.4x}
\end{equation}

And so the final lower bound can be written as

\begin{equation*}
\mathbb{E}_{\nu}[\tau] \geq \Big( \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m]})} \Big) \log \big(\frac{1}{2.4\delta} \big).
\end{equation*}

```{r, echo = FALSE}
x <- seq(0,1,by = 0.001)
bre <- function(x) x * log(x/(1-x)) + (1-x) * log((1-x)/x)
plot(x,bre(x), type = "l", ylab = "Binary Relative Entropy")
lines(x, log(1/(2.4*x)), col = "red")
abline(v = 0.15, lty = 2)
```

Given this general lower bound for the sampling complexity, or expected number of draws, it makes sense to define the complexity of a Top-$m$ bandit problem using the Kullback-Leibler divergence. After all, besides the number of arms and the experimenter-chosen confidence, it is just how close arms are with respect to each other in terms of Kullback-Leibler divergence that influences the sampling complexity.

Thus, following Kaufmann et al. (2016), define the complexity $\kappa_C(\nu)$ for the fixed confidence setting as

\begin{equation}
\kappa_C(\nu) = \inf_{A \, \text{PAC}} \lim_{\delta \to 0} \sup \frac{\mathbb{E}_{\nu}[\tau_{\delta}]}{\log \frac{1}{\delta}}.
\end{equation}

By plugging in the lower bound on the sampling complexity, we arrive at a complexity measure that depends only on the Kullback-Leibler measuring for each arm how far it is away from the border between the two groups of arms. To see this, consider the lower bound on the complexity measure given in Kaufmann et al. (2016):

@@

Given this description, we can already note that an intuitive extension of this complexity notion to the thresholding bandit problem might involve replacing $\mu_{[m]}$ and $\mu_{[m+1]}$ by the actual threshold $\tau$ (notation in Locatelli et al.) that divides the group above the threshold from the group below the threshold. In this sense, the previously used $\alpha$ is similar to the $\epsilon$ used in Locatelli et al. (2016).

Before we get to an extension of the thresholding bandit problem, however, at least two important steps remain. First, we need to define a complexity for the fixed budget problem. Second, we need to create algorithms that can match the lower bound.

Kaufmann et al. are able to provide a bound on their complexity measure in the fixed budget case, however only in the case of **two-armed** bandit models. As demanded in their paper, a fixed-budget algorithm is called consistent if the failure probability $p_t(\nu) := \mathbb{P}_{\nu}(\hat{S}_m \neq S^*_m)$ tends to zero as the number of samples goes to infinity. Also, define the complexity in the fixed-budget setting as follows:

@@

Given this definition, one can interpret the bound given in Theorem 12 of Kaufmann et al. directly as a lower bound on the complexity $\kappa_B(\nu)$ (note the inverse).

\begin{theorem}[Theorem 12, Kaufmann et al., 2016] \label{theorem:KaufmannEtAlTheorem12}
Let $\nu = (\nu_1, \nu_2)$ be a two-armed bandit model such that $\mu_1 > \mu_2$. In the fixed-budget setting, any consistent algorithm satisfies:

@@

For a proof, consider first the two different bandit models, $\nu$ and $\nu'$, where we fix without loss of generality that $a^* = 1$ is the best arm in $\nu$, while $a^* = 2$ in $\nu'$. Note that in this case we don't necessarily try to fool the algorithm by a change of distribution. Indeed, we want the algorithm $\mathcal{A}$ to be consistent for both problems. Since we are in the fixed-budget setting, the stopping time is fixed at $\tau = t$. Even though the correct decision differs between the two problems, we focus on the event $A = (\hat{S}_1 = 1)$. Given the formulation in Kaufmann et al. (2016), we have $A \in \mathcal{F}_t = \mathcal{F}_{\tau}$. Now, we can apply Lemma 1 as before, as it in essense gives a measure of how different two bandit models are. Here, we want to know how different $\nu$ is from $\nu'$, and so, given we have only two arms,

@@

The expectations were chosen with respect to $\nu'$ in order to allow the for the following: We have $p_t(\nu) = 1 - \mathbb{P}_{\nu}(A)$ and $p_t(\nu') = \mathbb{P}_{\nu'}(A)$ (since $A$ is wrong in $\nu'$). But since algorithm $\mathcal{A}$ is consistent for both $\nu$ and $\nu'$, we know that there should exist some number of samples such that the probability of event $A$ is bigger in setting $\nu$ (where it is the correct decision), than in setting $\nu'$ (where this would be a wrong decision and failure). Thus, for every $\epsilon > 0$, there exists $t_0(\epsilon)$ such that for all $t \geq t_0(\epsilon)$, $\mathbb{\nu'}(A) \leq \epsilon \leq \mathbb{P}_\nu(A)$. Consequently, if we plug in the bound of $\epsilon$ for $\mathbb{P}_{\nu'}(A)$, then

@@

Note that while deriving the lower bound on the complexity measure, we have also derived the following lower bound on the failure probability for the two-armed fixed-budget bandit:

@@

**Mention something about the fact that we were not able to do this for more than 2 arms and top-m bandits. How could it be extended to that? How could it be extended to the threshold bandit?**

As noted by Kaufmann et al. (2016), the advantage of this lower bound is that it makes the complexity in the fixed-confidence and the fixed-budget setting directly comparable. The disadvantage of course being that the result only holds for two-armed models. While the authors were not able to derive directly comparable lower bounds for the Top-$m$ case, they did derive a first lower bound in the Gaussian case with equal variances. While we would like to move beyond Gaussian distributions in the work at hand, the idea for the proof might show a way of how the ideas can be transferred to the thresholding bandit problem. We first state the result and then discuss the proof.

\begin{lemma}[Lemma 15, Kaufmann et al., 2016] \label{theorem:KaufmannEtAlLemma15}
Let $\nu$ and $\nu'$ be two bandit models such that $S^*_m(\nu) \neq S*_m(\nu')$. Then

\begin{equation*}
H +(\nu) = \sum_{a=1}^m \frac{2\sigma^2}{(\mu_a - \mu_{m+1})^2}, \quad H^-(\nu) = \sum_{a=m+1}^K \frac{2\sigma^2}{(\mu_m - \mu_a)^2} \quad
and \quad
H(\nu) = H^+(\nu) + H^-(\nu).
\end{equation*}

There exists $a \in {1, \dots, m}$ and $b \in \{m+1, \dots, K\}$ such that the bandit model $\nu^{[a,b]}$ described in Figure 4 (Kaufmann et al., 2016) satisfies $H(\nu^{[a,b]}) < H(\nu)$ and is such that

Given that we are again in the Top-$m$ setting, the proof idea is similar to the proof of Theorem \ref{theorem:KaufmannEtAlTheorem4} in that we again consider problems where we switch arms around the limit seperating the two groups of arms as given implicitly by $\mu_{[m]}$ and $\mu_{[m+1]}$. The hope here being that these methods could be applied to the thresholding bandit problem where the threshold of course gives the limit between the arms above and below the threshold. As we have seen in chapter 1, this flip around the threshold was of course used in the proof of the lower bound in Theorem 1 of Locatelli et al. (2016). However, there, again, the distributions were assumed to be Gaussian. This brings the big advantage that the Kullback-Leibler divergence becomes symmetric, and the feedback can take values on all $\mathbb{R}$. And by using the complexity measure $H(\nu)$, it is also clear that there exists an arm that is undersampled with respect to its contribution to the overall complexity of the problem (or sampled exactly according to its contribution), which leads to a convenient upper bound on this arms number of draws which is again employed in both the proof of Theorem \ref{theorem:KaufmannEtAlTheorem17} and in Locatelli et al. (2016). It is not clear yet, whether the same can also be done with other complexity measures.

We do not repeat the proof here for now.

See p20!

What remains is to present algorithms that are able to match the lower bounds derived so far.

@@

Given these lower bounds, all that is left is to find algorithms which are able to match the complexity. Sadly, not straightforward for Bernoullis.

Kaufmann et al. (2016) do not present algorithms matching the lower bound of Theorem \ref{theorem:KaufmannEtAlTheorem17}. They do consider algorithms that connect to Theorem \ref{theorem:KaufmannEtAlTheorem4} and Theorem \ref{theorem:KaufmannEtAlTheorem12}.

Given that Locatelli et al. (2016), and thus the problem we mostly consider in this thesis, is in the fixed-budget setting, we are most interested in the matching strategies for Theorem \ref{theorem:KaufmannEtAlTheorem12}. However, given that the lower bound applies only to two-armed bandits, the algorithms are of limited practical interest. Furthermore, the algorithms proposed require knowledge that is in general not available upfront.

For the example of Gaussian distributions, the knowledge of the (potentially different) variance is assumed which enables a strategy that pulls each arm proportional to its variance.

Even worse is the case of Bernoulli two-armed bandit models where the proposed algorithm requires knowledge about the true parameters of the distributions. That this limits the practical interest is also noted by the authors of Kaufmann et al. (2016). Thus, they suggest to use uniform sampling strategies in the case of two-armed Bernoulli bandits, and show that there is not much to be lost by doing so.

Thus, Kaufmann et al. (2016) join a number of other papers like Audibert et al. (2010) and Kaufmann and Kalyanakrishnan (2013) which struggle to find matching strategies in the fixed-budget setting that do not rely on knowledge of parameters or the complexity of the problem.

In contrast, Kaufmann et al. (2016) are able to show that their complexity measure derived for the fixed-confidence setting, $\kappa_C(\nu)$, can be upper-bounded using the upper bound of the sample complexity (number of pulls) given for the KL-LUCB algorithm in Kaufmann and Kalyanakrishnan (2013). Consequently, in the case of exponential family bandits, the complexity $\kappa_C(\nu)$ is bounded as given in equation (6) in Kaufmann et al. (2016):

@@

## Optimal Best Arm Identification

>>>>

---
title: "Draft"
header-includes:
   #- \documentclass[a4paper,twoside,english]{article}
   - \usepackage[retainorgcmds]{IEEEtrantools}
   - \usepackage{bm}
   - \usepackage{amsmath}
   - \usepackage{bbm}
   - \usepackage{hyperref}
   - \usepackage[lined,boxed]{algorithm2e}
   - \newtheorem{theorem}{Theorem}
   - \newtheorem{definition}{Definition}
   - \newtheorem{lemma}{Lemma}
   - \newtheorem{corollary}{Corollary}
   - \newcommand{\KL}{\,\text{KL}}
   - \newcommand{\der}{\,\text{d}}
   - \newcommand*{\Alignyesnumber}{\refstepcounter{equation}\tag{\theequation}}%
   #- \usepackage[top=1.5cm, bottom=1.5cm, outer=5cm, inner=2cm, heightrounded, marginparwidth=2.5cm, marginparsep=2cm]{geometry}
   #- \usepackage{fontspec}
   #-   \setmainfont{Arial}
keep_tex: TRUE
output:
  pdf_document:
    number_sections: true
    keep_tex: true
    toc: true
    toc_depth: 2
    #latex_engine: xelatex
fontsize: 11pt
urlcolor: blue
---

@@

\IncMargin{1em}
\begin{algorithm}
\SetKwData{Left}{left}\SetKwData{This}{this}\SetKwData{Up}{up}
\SetKwFunction{Union}{Union}\SetKwFunction{FindCompress}{FindCompress}
\SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
\Input{$\tau$, $\epsilon$}
\Output{$\hat{S}_{\tau} = \{i \in \{1,...,K\}, \hat{\mu}_i(T) \geq \tau\}$}
\BlankLine
\emph{Pull each arm once}\;
\For{$t = K+1$ \KwTo $T$}{
  \emph{Pull arm $I_t = \arg \min_{i \in A} B_i^{APT}(t) = \arg \min_{i \in A} \sqrt{T_i(t)} (|\hat{\mu}_i(t) - \tau|+\epsilon)$}\;
  \emph{Observe reward $X_t \sim \nu_{I_t}$}\;
}
\caption{Anytime Parameter-free Thresholding Algorithm (Locatelli et al., 2016)}\label{alg:APT}
\end{algorithm}
\DecMargin{1em}

@@

As noted in Zhong et al. (2017), a simple requirement to correctly classify arms at the final round is the following. For every arm $i \in \{1, ..., K\}$ after the final round $T$, require
$$
\hat{\mu}_{i}(T) \geq \mu_i - \frac{\mu_i - \tau + \epsilon}{2} \quad \text{if} \quad \mu_i \geq \tau
$$
or
$$
\hat{\mu}_{i}(T) \leq \mu_i + \frac{\tau - \mu_i + \epsilon}{2} \quad \text{if} \quad \mu_i < \tau
$$
Or simply in terms of the gap between the arm and the threshold as used in the index by the APT algorithm:
$$
| \hat{\mu}_{i}(T) - \mu_i | \leq \frac{|\mu_i - \tau| + \epsilon}{2} = \frac{\Delta_i}{2}.
$$

Intuitively, this condition makes sense as it ensures that the current mean estimate is closer to the true mean than to the threshold. Consequently, there is no arrangement possible in which the arm is classified wrong while the separation condition holds. Assuming $\mu_i < \tau$ and $\epsilon = 0$, an incorrect classification would require $\mu_i < \tau \leq \hat{\mu_i}$. But then  $| \hat{\mu}_{i}(T) - \mu_i | \geq |\mu_i - \tau|$, which violates the separation condition.

@@

Furthermore, we have assumed $T>2K$ in the statement of Theorem \ref{theorem:LocatelliTheorem4}. Plugging this in gives 
$$
T_k(T) - 1 \geq \frac{(T-K)h_k}{H} \geq \frac{(T-1/2T)h_k}{H} = \frac{Th_k}{2H}
$$

@@

$$
T_k(t) \geq T_k(T) - 1 \geq \frac{Th_k}{2H}.
$$

@@

$$
\mathbb{E}[\mathcal{L}(T)] = 1 - \mathbb{P}(\xi) \leq 2(\log(T)+1)K \exp(-\frac{1}{64R^2}\frac{T}{H}).
$$

@@

When introducing the thresholding bandit setting, we did not mention the fact that the budget $T$ does not need to be fixed upfront. Indeed, the setting in which the budget is *not* fixed upfront might be more popular among the best arm identification and top-$m$ literature. This setting is called *fixed confidence*, while the setting we considered so far is called *fixed budget*. In the fixed budget setting, we run algorithms for $T$ samples and then compare them based on their expected loss, $\mathbb{E}[\mathcal{L}(T)] = \mathbb{P}(\mathcal{S}^*_m \neq \hat{\mathcal{S}}_m) =: p_t(\nu)$ as we have seen in $\autoref{sec:Setup}$. Alternatively, consider a $\delta$-PAC strategy $\mathcal{A}(\delta)$for which holds for every problem $\nu \in \mathcal{M}_m$ that the classification holds at least with confidence level $1-\delta$, that is, $\mathbb{P}(\mathcal{S}^*_m = \hat{\mathcal{S}}_m) \geq 1-\delta$. The strategy has to achieve this level of confidence in its prediction before it is allowed to stop sampling. This is the fixed confidence case, in which the budget $T$ is no longer fixed upfront, but becomes a random variable. We compare algorithms by their expected number of draws $\mathbb{E}_{\nu}[T_{\delta}]$ and prefer those which arrive at the confidence level $1-\delta$ with a smaller expected budget.

@@

To prove this statement for a given $\delta$-PAC algorithm $\mathcal{A}$, we assume certain continuity conditions (compare Kaufmann et al. (2016)), with which there exists for every arm $a \in \{1, \dots, K\}$ an alternative model $\nu' = (\nu_1, \dots, \nu_{a-1}, \nu_a', \nu_{a+1}, \dots, \nu_K)$. In this alternative model, in accordance with the continuity conditions, only arm $a$ is modified. After the modification, the arm $\nu_{m+1}$ is now closer to $\nu_a$ as measured by the Kullback-Leibler divergence than $\nu_a'$ is to $\nu_a$, if $\mu_a > \mu_{m+1}$ (consequently, $\mu_a' < \mu_{m+1}$). On the other hand, if $\mu_a < \mu_{m}$, then $\nu_a'$ will be moved away from $\nu_a$ just enough so that $\nu_a$ is closer to $\nu_m$ than to $\nu_a'$ (consequently, $\mu_a' > \mu_m$). These changes in distribution make the original set of optimal arms, $\{1,\dots,m\}$, no longer optimal under the alternative model $\nu'$. To compare this to the thresholding bandit problem, assume that arms $\nu_{m}$ and $\nu_{m+1}$ indirectly define a threshold $\tau \in (\mu_{m+1},\mu_m)$. Then, by creating an alternative problem as described here, we flip arm $a$ around the implied threshold $\tau$ (compare the lower bound proof in \autoref{sec:AppendixAPTLB}).

Given that the strategy returns $\hat{S}_m$, we know that for the event $\mathcal{E} = (\hat{S}_m = \{1, \dots, m\})$ (which is element of the $\sigma$-Algebra $\mathcal{F}_{T}$ induced by the stopping time $T$), that $\mathbb{P}_{\nu}(\mathcal{E}) \geq 1-\delta$ and $\mathbb{P}_{\nu'}(\mathcal{E}) \leq \delta$ (because fixed confidence $\delta$!). To now give the lower bound on the expected number of samples, $\mathbb{E}_{\nu}[\tau]$, we employ the general Lemma given by the authors for such changes in distribution in bandit models.

@@

\begin{equation*}
\mathbb{E}_{\nu}[T] = \sum_{a=1}^K \mathbb{E}_{\nu}[N_a] \geq \Big( \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m]})} \Big) \der(1-\delta, \delta)
\end{equation*}

Given that we will be naturally interested in either very high or very low confidence of our algorithm, that is, $P_\nu(\mathcal{E})$ is either close to 0 or 1, it is possible to use the following approximation to the binary relative entropy given in Kaufmann et al. (2016):

\begin{equation}\label{bre_approx}
\forall x \in [0,1], \quad \der(x,1-x) = \der(1-x,x) \geq \log \frac{1}{2.4x}.
\end{equation}

This allows us to write the lower bound on the expected stopping time as:

\begin{equation*}
\mathbb{E}_{\nu}[T] \geq \Big( \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m]})} \Big) \log \big(\frac{1}{2.4\delta} \big).
\end{equation*}

Given this lower bound, it becomes clear that the complexity of the top-$m$ problem can be lower bounded by the Kullback-Leibler divergence between arms and the implied threshold between the $m$-th best arm and the $(m+1)$-th best arm. After all, the latter gives a lower bound on the effort (in terms of expected number of samples) required to achieve a certain confidence level. And a problem that requires a larger effort can be described as more complex. Indeed, in the case of fixed confidence problems, Kaufmann et al. (2016) describe problems as having a larger *sampling complexity*.

Following Kaufmann et al. (2016), we can now define the complexity $\kappa_C(\nu)$ for the fixed confidence setting as

\begin{equation}
\kappa_C(\nu) = \inf_{A \, \text{PAC}} \lim_{\delta \to 0} \sup \frac{\mathbb{E}_{\nu}[T{\delta}]}{\log \frac{1}{\delta}}. \label{eq:KappaC}
\end{equation}

This definition makes sense if we consider the fact that the confidence level $\delta$ is experimenter chosen and thus not relevant in describing the complexity. Thus, by including $\log(1/\delta)$ explicitly in \eqref{eq:KappaC}, we get rid of the confidence term in the lower bound on $\mathbb{E}_{\nu}[T]$ after plugging it into \eqref{eq:KappaC}. We arrive at the lower bound on the complexity measure given in Kaufmann et al. (2016):

@@

Given this description, we would expect that a complexity measure in a fixed confidence thresholding bandit probem might involve replacing $\mu_{[m]}$ and $\mu_{[m+1]}$ by the actual threshold $\tau$ that divides the group above the threshold from the group below the threshold.

However, given the problem formulation in Locatelli et al. (2016), we are mainly interested in complexity measures and algorithms for the fixed budget setting. As we will see now, the results of Kaufmann et al. (2016) are more limited for this case. While the authors are able to provide a bound on their complexity measure in the fixed budget case, it only applies to the case of *two-armed* bandit models. Consider a consistent fixed budget strategy $\mathcal{A}$ ($p_t(\nu)$ tends to zero as $t \rightarrow \infty$), and define the complexity in the fixed budget setting as follows:

@@

While we included the experimenter-fixed $\delta$ in the definition of $\kappa_C$, we now include the experimenter-fixed $T$ in the definition of $\kappa_B$ to disregard it in the complexity measure after plugging in the lower bound on $p_t(\nu)$. The resulting lower bound given in Theorem 12 of Kaufmann et al. (2016):

\begin{theorem}[Theorem 12, Kaufmann et al., 2016] \label{theorem:KaufmannEtAlTheorem12}
Let $\nu = (\nu_1, \nu_2)$ be a two-armed bandit model such that $\mu_1 > \mu_2$. In the fixed budget setting, any consistent algorithm satisfies:

@@

For a proof, consider first the two different bandit models, $\nu$ and $\nu'$, where we fix w.l.o.g. $a^* = 1$ as the best arm in $\nu$, while $a^* = 2$ in $\nu'$. Note that in this case we don't necessarily try to fool the algorithm by a change of distribution. Indeed, we want the algorithm $\mathcal{A}$ to be consistent for both problems. Since we are in the fixed budget setting, the stopping time is fixed at $T = t$. Even though the correct decision differs between the two problems, we focus on the event $A = (\hat{S}_1 = 1)$. Now, we can apply Lemma 1 as before, as it in essence gives a measure of how different two bandit models are. Here, we want to know how different $\nu$ is from $\nu'$, and so, given we have only two arms,

@@

The expectations were chosen with respect to $\nu'$ in order to allow for the following: We have $p_t(\nu) = 1 - \mathbb{P}_{\nu}(A)$ and $p_t(\nu') = \mathbb{P}_{\nu'}(A)$ (since $A$ is wrong in $\nu'$). But since algorithm $\mathcal{A}$ is consistent for both $\nu$ and $\nu'$, we know that there should exist some number of samples such that the probability of event $A$ is bigger in setting $\nu$ (where it is the correct decision) than in setting $\nu'$ (where this would be a wrong decision and failure). Thus, for every $\epsilon > 0$, there exists $t_0(\epsilon)$ such that for all $t \geq t_0(\epsilon)$, $\mathbb{P}_{\nu'}(A) \leq \epsilon \leq \mathbb{P}_\nu(A)$. Consequently, if we plug in the bound of $\epsilon$ for $\mathbb{P}_{\nu'}(A)$, then

@@

Note that while deriving the lower bound on the complexity measure, we have also derived the following lower bound on the failure probability for the two-armed fixed budget bandit:

@@

As noted by Kaufmann et al. (2016), the advantage of this lower bound is that it makes the complexity in the fixed confidence and the fixed budget setting directly comparable. The disadvantage of course being that the result only holds for two-armed models. While the authors are not able to derive directly comparable lower bounds for the top-$m$ case, they derive a first lower bound in the Gaussian case with equal variances, which we describe shortly in the appendix in \autoref{sec:KaufmannLBTopMGaussian}.

Before we discuss the strategies of Kaufmann et al. (2016) matching the lower bounds, we now show how lower bounds can be derived very similarly for the fixed budget thresholding problem.

### Lower Bound for Fixed Budget Thresholding Problem

In order to derive a bound for the fixed budget problem, Kaufmann et al. (2016) have focused on the case of the two-armed bandit which is the most simple version of the top-$m$ problem. Less than two arms do not make sense, since then this single arm will always be the best arm. In the case of the thresholding bandit, however, a single-armed problem makes still some sense in that we still have to classify this arm correctly with respect to the threshold. Thus, we can show the following corollary which gives the a bound on the complexity of the single-armed thresholding bandit.

\begin{corollary}
Let $\nu = \nu_1$ be a one-armed thresholding bandit model where $\tau$ is the threshold fixed upfront. Let $\nu$ be from the univariate canonical exponential family of distributions such that it can be parameterized by its mean, $\mu_1$, and the Kullback-Leibler divergence between distributions $\nu_1$ and $\nu_1'$ can be written as $\KL(\nu_1', \nu_1) = \KL(\mu_1', \mu_1)$. In the fixed budget setting, any consistent algorithm satisfies:

$$
- \frac{1}{t} \log p_t(\nu) \leq \KL(\tau, \mu_1)
$$
\end{corollary}

This of course is basically the Chernoff-Stein Lemma for the hypothesis test of two alternatives (compare chapter 11 in Cover and Thomas, 2006).

But as we see in the following corollary, we can extend the lower bound to the $K$-armed fixed budget thresholding bandit problem, which stands in contrast to the fact that for the top-$m$ problem, it is only possible to show the lower bound for two arms.

\begin{corollary}
Let $\nu = (\nu_1, ..., \nu_K)$ be a $K$-armed thresholding bandit problem in which $\tau$ is the threshold fixed upfront. For $i \in \{1,...,K\}$, let $\nu_i$ be from the univariate canonical exponential family of distributions such that it can be parameterized by its mean, $\mu_i$, and the Kullback-Leibler divergence between distributions $\nu_i$ and $\nu_i'$ can be written as $\KL(\nu_i, \nu_i') = \KL(\mu_i, \mu_i')$. In the fixed budget setting, every consistent algorithm satisfies:

$$
\lim_{t \rightarrow \infty} -\frac{1}{t} \log p_t(\nu) \leq \max_{a \in \{1,...,K\}} \KL(\tau, \mu_a)
$$
\end{corollary}

Given the lower bounds on the sampling complexity and error probability, as well as the complexity measures, we now turn to sampling strategies that are designed to match these lower bounds.

@@

Kaufmann et al. (2016) do not present algorithms matching the lower bound of Theorem \ref{theorem:KaufmannEtAlTheorem17}. They do consider algorithms that connect to Theorem \ref{theorem:KaufmannEtAlTheorem4} and Theorem \ref{theorem:KaufmannEtAlTheorem12}. Given that we aim to extend the fixed budget thresholding bandit problem, we are most interested in the matching strategies for Theorem \ref{theorem:KaufmannEtAlTheorem12}. However, given that this lower bound applies only to two-armed bandits, the algorithms proposed by Kaufmann et al. (2016) are of limited practical interest. Furthermore, the proposed strategies require knowledge that is in general not available upfront: For Gaussian distributions, the knowledge of the (potentially different) variance is assumed which enables a strategy that pulls each arm proportional to its variance.

Even more difficult are the assumptions in the case of Bernoulli two-armed bandit models: The proposed algorithm requires knowledge about the true parameters of the distributions. That this limits the practical interest is also noted by the authors of Kaufmann et al. (2016). Thus, they suggest to use uniform sampling strategies in the case of two-armed Bernoulli bandits, and show that there is not much to be lost by doing so.

Thus, Kaufmann et al. (2016) join a number of other papers like Audibert et al. (2010) and Kaufmann and Kalyanakrishnan (2013) which struggle to find matching strategies in the fixed budget setting that do not rely on knowledge of parameters or the complexity of the problem.

In contrast, Kaufmann et al. (2016) are able to show that their complexity measure derived for the fixed confidence setting, $\kappa_C(\nu)$, can be upper-bounded using the upper bound given for the KL-LUCB algorithm in Kaufmann and Kalyanakrishnan (2013). Consequently, in the case of exponential family bandits, the complexity $\kappa_C(\nu)$ is bounded as given in equation (6) in Kaufmann et al. (2016):

@@

## Optimal Best Arm Identification \label{sec:OptimalBestArmIdentification}
